```{r setup, include=FALSE}
library(sourcetools)
library(microbenchmark)
```

[![Travis-CI Build Status](https://travis-ci.org/kevinushey/sourcetools.svg?branch=master)](https://travis-ci.org/kevinushey/sourcetools) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/kevinushey/sourcetools?branch=master&svg=true)](https://ci.appveyor.com/project/kevinushey/sourcetools)


# sourcetools

Tools for reading, tokenizing, and (eventually) parsing `R` code.

## Getting Started

You can install `sourcetools` from CRAN with:

```{r, eval=FALSE}
install.packages("sourcetools")
```

Or, you can install the development version from GitHub with:

```{r, eval=FALSE}
devtools::install_github("kevinushey/sourcetools")
```

## Reading

`sourcetools` comes with a couple fast functions for reading
files into `R`.

Use `read()` and `read_lines()` to quickly read a file into
`R` as character vectors. `read_lines()` handles both
Windows style `\r\n` line endings, as well as Unix-style
`\n` endings. Performance is on par with the readers
provided by the
[readr](https://cran.r-project.org/package=readr) package.

```{r}
text <- replicate(10000, {
  paste(sample(letters, 200, TRUE), collapse = "")
})
file <- tempfile()
cat(text, file = file, sep = "\n")
mb <- microbenchmark::microbenchmark(times = 10,
  base::readLines(file),
  readr::read_lines(file),
  sourcetools::read_lines(file)
)
sm <- summary(mb)
print(sm[c("expr", "mean", "median")], digits = 3)
unlink(file)
```

## Tokenization

`sourcetools` provides the `tokenize_string()` and
`tokenize_file()` functions for generating a tokenized
representation of R code. These produce 'raw' tokenized
representations of the code, with each token's value as a
string, and a recorded row, column, and type:

```{r}
tokenize_string("if (x < 10) 20")
```
