```{r setup, include=FALSE}
library(sourcetools)
```

[![Travis-CI Build Status](https://travis-ci.org/kevinushey/sourcetools.svg?branch=master)](https://travis-ci.org/kevinushey/sourcetools) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/kevinushey/sourcetools?branch=master&svg=true)](https://ci.appveyor.com/project/kevinushey/sourcetools)


sourcetools
===========

Tools for tokenizing and (eventually) parsing R code.

## Getting Started

`sourcetools` is not yet on CRAN -- install with

```{r, eval=FALSE}
devtools::install_github("kevinushey/sourcetools")
```

## Tokenization

`sourcetools` provides the `tokenize_string()` and
`tokenize_file()` functions for generating a tokenized
representation of R code. These produce 'raw' tokenized
representations of the code, with each token's value as a
string, and a recorded row, column, and type:

```{r}
tokenize_string("if (x < 10) 20")
```

## Syntax Validation

`validate_syntax()` is provided to identify syntax errors:

```{r}
validate_syntax("{1 + 2)")
```
